|

### 2021-02-03 paper/reviews_ds.Rmd

Sincerely, on behalve of all coauthors,
Caspar van Lissa

@@

With regard to the specific platforms named by the Reviewer:
We are not aware of arguments to support a strong preference for Zenodo or FigShare over GitHub.
Without such arguments, as far as we are concerned, these repositories are largely interchangeable.
One key advantage of storing the data on GitHub is that they are then bundled with the
documentation (e.g., codebook), analysis code, and manuscript.
Thus, readers have access to **all** materials required for replication in one repository.
Moreover, the entire project can be readily updated from the console, and is version controlled.
GitHub additionally offers user interaction with the materials through
forking, cloning, opening issues, and sending pull requests -
all useful tools for replication and collaboration.

>>>>

Sincerely, on behalf of all coauthors,
Caspar van Lissa

@@

With regard to the specific platforms named by the Reviewer:
The nature of a repository created by worcs is initially a living project, for which the worcs package automates the workflow.
This workflow includes version control through git, for which remote storage at Github (or similar websites) is a logical extension that fits the workflow.
<!--We are not aware of arguments to support a strong preference for Zenodo or FigShare over GitHub.
Without such arguments, as far as we are concerned, these repositories are largely interchangeable. BV I disagree with this: they are very different repositories that do very different things, and for our purposes GH is clearly the one to go to. It's not a toss-up!-->
One key advantage of storing the data on GitHub as well, as part of the project, is that they are then bundled with the
documentation (e.g., codebook), analysis code, and manuscript.
Thus, readers have access to **all** materials required for replication in one repository.
Moreover, the entire project can be readily updated from the console, and is version controlled.
GitHub additionally offers user interaction with the materials through
forking, cloning, opening issues, and sending pull requests -
all useful tools for replication and collaboration.
